Drivers of sex differences in consumption

### 2017-03-13 sex-difference/sex-difference.Rmd
sex differences

usage %>%
  mutate(age_group=bounds_group(age, c(65, 75, 85, 95))) %>%
  group_by(age_group, sex, bene_id) %>%
  summarize_at(vars(n_claims, n_days), sum) %>%
  summarize(mean_n_claims=mean(n_claims),
            mean_n_days=mean(n_days),
            n_bene=n()) %>%
  kable
```

@@

>>>>

usage %>%
  filter(sex %in% c('male', 'female')) %>%
  mutate(age_group=bounds_group(age, c(65, 75, 85, 95))) %>%
  group_by(age_group, sex, bene_id) %>%
  summarize_at(vars(n_claims, n_days), sum) %>%
  summarize(mean_n_claims=mean(n_claims),
            mean_n_days=mean(n_days),
            n_bene=n()) %>%
  kable
```

@@

Does that mean that:

- women are older and therefore use more azithromycin,
- women have more chronic conditions (esp. COPD) and therefore use more, or
- women have more encounters with doctors and therefore are prescribed more?

### Sex by age

The older people are more female: age 65 is about 60% female. This stays constant around 60% (or dips slightly) until age 75, when it steadily increases up to 85-90% female at age 100. So we'll need to account for this age difference.

```{r}
plot_dat = usage %>%
  select(age, sex) %>%
  filter(sex %in% c('male', 'female')) %>%
  group_by(age) %>% count(sex) %>% ungroup() %>%
  spread(sex, n, fill=0L) %>%
  mutate(total=female+male, grand_total=sum(total),
         fraction_year=total/grand_total, fraction_female=female/total)

ggplot(mapping=aes(x=age, y=fraction)) +
  geom_point(data=rename(plot_dat, fraction=fraction_female)) +
  geom_line(data=mutate(plot_dat, fraction=fraction_year*10), col='red') +
  ylab('fraction female') + ylim(0, 1) +
  theme_minimal()
```

### Chronic conditions

Cf. the chronic conditions report.

### Encounters by sex

Do women have more encounters than men? Does that explain their increased usage?

```{r load_carrier_data}
carrier = read_tsv('../../data/carrier_count_2011.tsv') %>%
  rename(bene_id=BENE_ID, n_carrier_dates=n_from_dates)

inpatient = read_tsv('../../data/inpatient_count_2011.tsv') %>%
  rename(bene_id=BENE_ID, n_inpatient_dates=n_from_dates)

outpatient = read_tsv('../../data/outpatient_count_2011.tsv') %>%
  rename(bene_id=BENE_ID, n_outpatient_dates=n_from_dates)

denom = usage %>% select(bene_id, sex, age) %>% distinct
```

```{r azithromycin_usage}
na_to_zero = function(x) if_else(is.na(x), 0L, x)

azi_usage = usage %>%
  filter(antibiotic=='azithromycin') %>%
  group_by(bene_id) %>%
  summarize(n_claims=sum(n_claims)) %>%
  left_join(denom, by='bene_id') %>%
  filter(age >= 65, sex %in% c('male', 'female')) %>%
  left_join(carrier, by='bene_id') %>%
  left_join(inpatient, by='bene_id') %>%
  left_join(outpatient, by='bene_id') %>%
  mutate(age_group=bounds_group(age, c(65, 75, 85, 95))) %>%
  mutate_at(vars(n_claims, n_carrier_dates, n_inpatient_dates, n_outpatient_dates), na_to_zero)
```

```{r azithromycin_usage_table}
azi_usage %>%
  group_by(age_group, sex) %>%
  summarize(n_beneficiaries=n(),
            mean_n_azithromycin_claims=mean(n_claims),
            med_n_carrier_dates=median(n_carrier_dates),
            med_n_outpatient_dates=median(n_outpatient_dates),
            med_n_inpatient_dates=median(n_inpatient_dates)) %>%
  kable
```

And I'll do a Poisson regression of number of azithromycin claims against age, being female, and number of carrier dates:

```{r azithromycin_usage_model}
library(broom)
azi_usage %>%
  mutate(is_female=sex=='female') %>%
  glm(n_claims ~ age + is_female + n_carrier_dates + n_inpatient_dates + n_outpatient_dates, data=., family='poisson') %>%
  tidy %>%
  mutate(pct.increase=round((exp(estimate)-1.0)*100, 2)) %>%
  kable
```

The coefficient for being female (0.05) accounts for almost the entire difference in consumption between men and women (56 per thousand). Note that age has an approximately zero correlation (i.e.,
